\documentclass{amsart}

\usepackage{enumitem}
\usepackage{mathtools}

\theoremstyle{definition}
\newtheorem{exercise}{Exercise}

\DeclarePairedDelimiter\abs{\lvert}{\rvert} % absolute value
% Swap the definition of \abs*, so that \abs
% resizes the size of the bars, and the starred version does not.
\makeatletter
\let\oldabs\abs%
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\makeatother

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\card}[1]{\abs{#1}}
\newcommand{\st}{\mathrel{:}}

\title{MATH 355: Homework 10}
\author{Alexander Lee}

\begin{document}

\maketitle

\begin{exercise}[5.3.2]
  Suppose $f(a) = f(b)$ for some $a, b \in A$. Suppose towards a contradiction
  that $a \neq b$. Without loss of generality, suppose $a < b$. By the Mean
  Value Theorem, since $f : [a, b] \to \R$ is continuous on $[a, b]$ and
  differentiable on $(a, b)$, there exists a point $c \in (a, b)$ where
  \[
    f'(c) = \frac{f(b) - f(a)}{b - a}.
  \]
  However, since $f(a) = f(b)$ and $b \neq a$, we have that $f'(c) = \frac{0}{b
  - a} = 0$. This is a contradiction, since we assumed that $f'(x) \neq 0$ for
  all $x \in A$. Thus, it must be that $a = b$ and therefore $f$ is one-to-one
  on $A$.

  To show that the converse statement need not be true, consider the
  differentiable function $f(x) = x^3$ on the interval $A = (-1, 1)$. Here,
  $f$ is clearly one-to-one, but $f'(0) = 0$.
\end{exercise}

\begin{exercise}[5.3.3 skip (c)]
  \begin{enumerate}[label={(\alph*)}]
    \item Consider the function $f(x) = h(x) - x$ defined on the interval $[0,
      3]$. To argue that there exists a point $d \in [0, 3]$ where $h(d) = d$,
      we show that there exists a point $d \in [0, 3]$ where $f(d) = 0$. First,
      consider
      \[
        f(0) = h(0) - 0 = 1 - 0 = 1.
      \]
      Then, consider
      \[
        f(3) = h(3) - 3 = 2 - 3 = -1.
      \]
      Also notice that because $h$ is differentiable on $[0, 3]$, $h$ is also
      continuous on $[0, 3]$. It follows from the Algebraic Continuity Theorem
      that $f(x) = h(x) - x$ is also continuous on $[0, 3]$. Since $f$ is
      continuous on $[0, 3]$ and $f(3) = -1 < 0 < 1 = f(0)$, there exists a
      point $d \in (0, 3)$ where $f(d) = 0$ by the Intermediate Value Theorem.
      It follows that there exists a point $d \in [0, 3]$ where $h(d) = d$.
    \item Since $h$ is differentiable on $[0, 3]$, $h$ is thus continuous on
      $[0, 3]$ and differentiable on $(0, 3)$. Then, by the Mean Value Theorem,
      there exists a point $c \in (0, 3)$ where
      \[
        h'(c) = \frac{h(3) - h(0)}{3 - 0} = \frac{2 - 1}{3} = \frac{1}{3}.
      \]
  \end{enumerate}
\end{exercise}

\begin{exercise}[5.3.4]
  \begin{enumerate}[label={(\alph*)}]
    \item Because $f$ is differentiable on $A$, $f$ is also continuous on $A$.
      By the Characterizations on Continuity, since $(x_n) \to 0$, it follows
      that $f(x_n) \to f(0)$. Because $f(x_n) = 0$ for all $n \in \N$, it must
      be that $f(0) = 0$. Furthermore, since $f$ is differentiable at zero, we
      have that
      \[
        f'(0) = \lim_{x \to 0} \frac{f(x) - f(0)}{x - 0}.
      \]
      By the Sequential Criterion for Functional Limits, we also have that
      \[
        f'(0) = \lim \frac{f(x_n) - f(0)}{x_n - 0} = \lim \frac{0 - 0}{x_n} =
        \lim \frac{0}{x_n} = 0.
      \]
    \item Without loss of generality, suppose that $x_n > 0$ for all $n \in \N$.
      Then, by the Mean Value Theorem, there exists a point $c_n \in (0, x_n)$
      such that
      \[
        f'(c_n) = \frac{f(x_n) - f(0)}{x_n - 0} = \frac{0 - 0}{x_n} =
        \frac{0}{x_n} = 0
      \]
      for all $n \in \N$. Since $f$ is twice-differentiable at zero, we have
      that
      \[
        f''(0) = \lim_{x \to 0} \frac{f'(x) - f'(0)}{x - 0}.
      \]
      By the Squeeze Theorem, we have that $(c_n) \to 0$. Thus, it follows from
      the Sequential Criterion for Functional Limits that
      \[
        f''(0) = \lim \frac{f'(c_n) - f'(0)}{c_n - 0} = \frac{0 - 0}{c_n} =
        \frac{0}{c_n} = 0.
      \]
  \end{enumerate}
\end{exercise}

\begin{exercise}[6.2.1]
  \begin{enumerate}[label={(\alph*)}]
    \item Given $x \in (0, \infty)$, we have that
      \[
        \lim f_n(x) = \lim \frac{nx}{1 + nx^2} = \lim \frac{x}{1/n + x^2} =
        \frac{x}{x^2} = \frac{1}{x}
      \]
      by the Algebraic Limit Theorem.
      Thus, the pointwise limit of $(f_n)$ for all $x \in (0, \infty)$ is $f(x)
      = \frac{1}{x}$.
    \item No. Observe that
      \[
        \abs{f_n(x) - f(x)} = \abs{\frac{nx}{1 + nx^2} - \frac{1}{x}} =
        \abs{\frac{nx^2 - (1 + nx^2)}{x(1 + nx^2)}} = \frac{1}{x(1 + nx^2)}.
      \]
      Then given $N \in \N$, choose $n \ge \N$ and $x = \frac{1}{n} \in (0,
      \infty)$. It follows that
      \[
        \abs{f_n(x) - f(x)} = \frac{1}{x(1 + nx^2)} = \frac{n}{1 + n \cdot
        \frac{1}{n^2}} = \frac{n}{1 + \frac{1}{n}} = \frac{n^2}{n + 1} \ge
        \frac{1}{2}.
      \]
      Therefore, the convergence is not uniform on $(0, \infty)$.
    \item No. Same reasoning as (b). Observe that the choice of $x =
      \frac{1}{n}$ is also in $(0, 1)$.
    \item Yes. Let $\epsilon > 0$ be arbitrary. Choose $N \in \N$ such that $N >
      \frac{1}{\epsilon}$. Then, whenever $n \ge N$ and $x \in (1, \infty)$, it
      follows that
      \[
        \abs{f_n(x) - f(x)} = \frac{1}{x(1 + nx^2)} < \frac{1}{1 + n} <
        \frac{1}{n} \le \frac{1}{N} < \epsilon.
      \]
  \end{enumerate}
\end{exercise}

\begin{exercise}[6.2.2]
  \begin{enumerate}[label={(\alph*)}]
    \item Each $f_n$ is continuous at zero. To see why, let $\epsilon > 0$ be
      arbitrary and choose $\delta < \frac{1}{n}$. Then, if $\abs{x} < \delta$,
      it follows that
      \[
        \abs{f_n(x) - f_n(0)} = \abs{f_n(x) - 0} = \abs{f_n(x)} = f_n(x) = 0 <
        \epsilon.
      \]

      We first show that $f$ is not continuous at zero. Since $x_n =
      \frac{1}{n}$ converges to 0 but $f(x_n)$ converges to $1 \neq 0 = f(0)$,
      it follows from the Criterion for Discontinuity that $f$ is not continuous
      at 0.

      We now show that $f_n \to f$ not uniformly on $\R$. By the contrapositive
      of the Continuous Limit Theorem, since $f$ is not continuous at zero and
      each $f_n$ is continuous at zero, it must be that $f_n \to f$ not
      uniformly on $\R$.
    \item Each $f_n$ is continuous at zero by the same argument from (a).

      To show that $g_n \to g$ uniformly on $\R$, Let $\epsilon > 0$ be
      arbitrary, choose $N \in \N$ and let $n \ge N$. If $x = \frac{1}{k}$ for
      some $k \in \N$ such that $k \le n$, then
      \[
        \abs{g_n(x) - g(x)} = \abs{\frac{1}{k} - \frac{1}{k}} = 0 < \epsilon.
      \]
      Otherwise, then
      \[
        \abs{g_n(x) - g(x)} = \abs{0 - 0} = 0 < \epsilon.
      \]

      We now show that $f$ is continuous at zero. Let $\epsilon > 0$ be
      arbitrary and choose $\delta = \epsilon$. If $\abs{x} < \delta$, it
      follows that
      \[
        \abs{g(x) - g(0)} = \abs{g(x) - 0} = \abs{g(x)} \le \abs{x} < \delta =
        \epsilon.
      \]
    \item Each $f_n$ is continuous at zero by the same argument from (a).

      TODO
  \end{enumerate}
\end{exercise}

\end{document}
